Work Fragmentation in Developer Interaction Data

### 2016-02-10 paper_2.tex
More results in RQ2

\usepackage{graphics}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{theorem}
\usepackage{verbatim} % comentarios
\usepackage{amsmath}
%\usepackage{algorithm}
%\usepackage{algpseudocode}
\usepackage{mwe}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage[export]{adjustbox}

\usepackage{array}
\newcommand\RR[1]{\textbf{Romain #1}}

@@

%First, we analyzed the number of interruptions over the productivity. In this sense, 
We split the data in five groups: The first group contains all the sessions without interruptions (\textit{none}). For the others groups, we have considered four ranges of number of interruptions delimited by their quartiles; the results differ between Mylyn and UDC, as there are more interruptions per session in the former (Table \ref{tbl:quartil_int}). Then, for each group, we display the distribution of events per minute and edit ratio via boxplots. We can see the results with Mylyn in Figure \ref{fig:box_int_events}), and for UDC in Figure \ref{fig:box_int_events_udc}.

@@

In this section we analyze whether or not the interruption duration is a factor in the relationship between interruptions and developer productivity. Under the hypothesis that prolonged interruptions require more time to recover, we have built three groups of sessions based on the proportion of long interruptions. As we described previously we consider prolonged interruption are those whose duration is $\geq$12 minutes, according to previous work \cite{GM04, KaptelininN07}. Prolonged interruptions could be due to an extended interruption, such as a coffee break or a meeting.

The proportion of long interruptions is calculated as the sum of interruptions longer than 11 minutes, divided by the total of interruptions in that session. Then, we obtain the quantiles of the distribution of this proportion and use them to create 3 groups described in the following:

\begin{itemize}
\item \textit{low}: the first group consists of sessions where the proportion of prolonged interruptions is $<$0.30; this includes sessions for which the proportion of long interruption is zero, that is, sessions with only short interruptions. These sessions constitute 47.7\% in Mylyn and 20.8\% in UDC, from the total of sessions in both datasets.
\item \textit{medium}: the second group consists of sessions with a higher proportion of long interruptions, between 0.30 and 0.50. These sessions constitute 31.8\% in Mylyn and 18.9\% in UDC.
\item \textit{high}: finally, more than half the sessions in the last group are pronlonger (proportion $>$0.50). This represents 20.5\% of the sessions in Mylyn and 60.1\% in UDC.
\end{itemize}

Following the conclusions on RQ1, the number of interruptions may affect the results if we ignore that variable. So, we split every group in accordance to the number of interruptions; this time, instead of taking the quantiles of the distribution we took the terciles \RR{Why?}. Thus, for the three metrics, we created the groups low, medium and high, and every group was split three additional groups according to the terciles of the distribution of the number on interruptions.

The Figure \ref{fig:lines_dur_int} shows the median of the metrics when grouping the sessions by the number of interruptions and the proportion of prolonged interruptions with Mylyn, and the Figure \ref{fig:udc_lines_dur_int} with UDC. In this context, it is better to have a low number of interruptions (group [1-3]) and a low proportion of prolonged interruptions, and the results agree with this statement. For example, when having between 1 to 3 interruptions and a low proportion the metrics show higher values when compared to having $>$ 6 interruptions and a high proportion of prolonged interruptions. Moreover, if we focus on a category we can see a gradual decrease as the number of interruptions increases, which lead us to conclude that the proportion of prolonged interruptions has an effect on the developer productivity. In the Figures the color of lines represent a classificacion of the proportion of prolonged interruptions, being the green line the 'low' type, blue the 'medium' and red the 'high'.

The difference between categories seems to decrease when reaching higher values. There is a clear difference between the low and medium categories of proportions, but the difference between medium and high is minor. The same happens when comparing the categories [1-3] and [4-6] of the number of interruptions, and the categories [4-6] and $>$6. In other words, as the value of the metrics get higher, the negative effect (according to these metrics) changes at a very low rhythm.

Comparing the results between the datasets, UDC seems to show a more defined difference between groups. The sessions with a low proportion of prolonged interruption has a greater difference (higher productivity) than sessions with medium proportion. In Mylyn this difference is more subtle but can be identified, although when having more than 6 interruptions there is not a real difference.

\begin{figure}[!ht]
	\centering
	\begin{tabular}{c}
		\minipage{1\textwidth}
		\includegraphics[width=\linewidth,clip=, angle=0]{figures/lines_dur_int}  \\
		\endminipage\hfill
	\end{tabular}
	\caption{Plot showing the median values for the metrics according to the proportion of prolonged interruptions and the number of interruptions in Mylyn. }
	\label{fig:lines_dur_int}
\end{figure}

\begin{figure}[!ht]
	\centering
	\begin{tabular}{c}
		\minipage{1\textwidth}
		\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_lines_dur_int}  \\
		\endminipage\hfill
	\end{tabular}
	\caption{Plot showing the median values for the metrics according to the proportion of prolonged interruptions and the number of interruptions in UDC. }
	\label{fig:udc_lines_dur_int}
\end{figure}

%\begin{table}
%\small
%\renewcommand{\arraystretch}{1.3}
%\caption{Median for the edits per minute, selections per minute and edit ratio according to the number of interruptions and the proportion of prolonged interruptions in UDC.}
%\label{tbl:udc_stats_dur_int}
%\centering
%\begin{tabular}{|p{3cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
%	  \hline 
%	  & \multicolumn{4}{c|}{Number of interruptions} \\
%	  \hline
%	Proportion of long int. & none & [1-3] & [4-6] & $>$6 \\  
%	  \hline 
%	\multicolumn{5}{c}{\textit{Edits per minute}} \\
%		\hline
%		low & 3.58 &  2.52 & 1.45 & 1.36 \\
%		\hline
%		medium & 3.58 & 1.25 & 1.15 &  1.27 \\		
%		\hline		
%		high  & 3.58 & 1.25 & 1 & 0.95   \\
%		\hline
%	\multicolumn{5}{c}{\textit{Selections per minute}} \\
%	    \hline 
%		low &  2.54& 2.15 & 1.6 & 1.44\\
%		\hline
%		medium & 2.54 & 1.5 & 1.5 & 1.41  \\
%		\hline				
%		high & 2.54&  1.55  & 1.45 & 1.36  \\
%	    \hline
%	 \multicolumn{5}{c}{\textit{Edit ratio}} \\
%	   \hline 
%		low & 0.57 & 0.54 & 0.47  & 0.46 \\
%		\hline
%		medium & 0.57 & 0.45 & 0.44 & 0.46  \\
%		\hline				
%		high & 0.57 & 0.46 & 0.42 & 0.44  \\
%	   \hline
%\end{tabular}
%\end{table}

The statistical tests show that...

\begin{table}[ht!]
\tiny
\renewcommand{\arraystretch}{1.3}
\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions in UDC} %, and editions and selections.}
\label{tbl:p_value2}
\centering
\begin{tabular}{l | p{0.7cm} | p{1cm} | p{1cm} | p{1cm} } 
  & none & low & medium & high  \\  
  \hline
  \multicolumn{5}{c}{\textbf{Edits}} \\
  \hline
  mean & 4.01 &	2.31 & 1.94 & 2.06 \\ 
  % \cline{3-4} 
  %t.test & $\hookrightarrow$& \multicolumn{2}{c}{$<$ 2.2e-16} \\
   \cline{3-5} 
  U-test & $\hookrightarrow$ & \multicolumn{3}{c}{$<$ 2.2e-16}  \\

  \cline{3-5} 
  Cohen's $d$ & $\hookrightarrow$	& \textbf{0.75} & \textbf{0.89} & \textbf{0.70}  \\
  \hline

  \multicolumn{5}{c}{\textbf{Selections}} \\
  \hline 
  mean & 2.99 &	2.08 & 1.85 & 1.97 \\ 
  % \cline{3-4} 
  %t.test & $\hookrightarrow$& 2.089e-08 & 8.175e-14 \\
   \cline{3-5} 
  U-test & $\hookrightarrow$ & 8.467e-13 & \multicolumn{2}{c}{$<$ 2.2e-16}  \\

  \cline{3-5} 
  Cohen's $d$ & $\hookrightarrow$	& \textbf{0.53} & \textbf{0.69} & \textbf{0.49} \\  
  \hline
  \multicolumn{5}{c}{\textbf{Edit ratio}} \\
  \hline 
  mean & 0.56 & 0.49 & 0.45 & 0.44 \\ 
%   \cline{3-4} 
%  t.test & $\hookrightarrow$&  4.20E-12 & $<$ 2.2e-16 \\
   \cline{3-5} 
  U-test & $\hookrightarrow$ & 6.467e-05 & 2.095e-08 & 1.218e-09 \\
  \cline{3-5} 
  Cohen's $d$ & $\hookrightarrow$ & \textbf{0.29} & \textbf{0.41} & \textbf{0.45}\\
\hline

@@

%In this section we analyze whether or not the interruption duration is a factor in the relationship between interruptions and developer productivity. To substantiate this claim, we have built two groups of sessions with interruptions:
%\item \textit{short}: the first group consists of sessions that only have short interruptions ($<$ 12 minutes of duration). These sessions constitute 18\% in Mylyn and 6\% in UDC, from the total of sessions in both datasets.
%\item \textit{prolonged}: the second group consists of the remaining sessions, which have at least one prolonged interruption ($\geq$ 12 minutes of duration). These session constitute 80\% in Mylyn and 93\% in UDC.
%\item \textit{none}: the sessions in this group do not contain interruptions, which are the 2\% in Mylyn and 1\% in UDC.
%We then displayed the distribution of events by minutes and edit ratio of these two groups and compared them with the sessions without interruptions The Figure \ref{fig:box_dur_events} shows the results for Mylyn and the Figure \ref{fig:box_dur_events_udc} for UDC. We observe that the number of events per minute is lower in sessions with at least one prolonged interruption. 
%\includegraphics[width=\linewidth,clip=, angle=0]{figures/box_plot_range_edit}  
%\includegraphics[width=\linewidth,clip=, angle=0]{figures/box_plot_range_sel}  
%\includegraphics[width=\linewidth,clip=, angle=0]{figures/box_dur_ratio}
%\caption{Boxplots showing the relation between the number of edits and selections per minute, the edit ratio and interruption duration in Mylyn}
%\label{fig:box_dur_events}
%\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_box_plot_range_edit}  \\
%\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_box_plot_range_sel}  \\
%\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_box_dur_ratio} \\
%\caption{Boxplots showing the relation between the number of edits and selections per minute, the edit ratio and interruption duration in UDC}
%With Mylyn, as in the previous case, the differences are significant, and we used \textit{Cohen's d} to measure the practical significance of the means (Table \ref{tbl:p_value2}). We note that the effect size of the interruption duration over the number of edits per minute is very large. In selections, the effect is moderate for short interruptions, and large for prolonged interruptions.
%The effect size test results in the Table \ref{tbl:p_value2_udc} correspond to the results with UDC, and matches the previous observations (RQ1) on a less pronounced effect compared to the Mylyn dataset. The Cohen's \textit{d} test results tell us that we can label the effect from medium to large and the median values act accordingly to our observations in Mylyn. Therefore, we conclude that the relationship between user activity and interruptions could be adversely affected by interruptions of longer duration. 
%\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions in Mylyn} %, and editions and selections.}
%\label{tbl:p_value2}
%  mean & 6.96 &	2.98 & 1.76 \\ 
%  U-test & $\hookrightarrow$ & \multicolumn{2}{c}{$<$ 2.2e-16}  \\
%  Cohen's $d$ & $\hookrightarrow$	& \textbf{1.23} & \textbf{2.11}   \\
%  mean & 5.20 &	3.33 & 2.47 \\ 
%  U-test & $\hookrightarrow$ & 6.197e-13 & $<$ 2.2e-16 \\
%  Cohen's $d$ & $\hookrightarrow$	& \textbf{0.63} & \textbf{1.24}  \\  
%  mean & 0.55 & 0.40 & 0.34\\ 
%  U-test & $\hookrightarrow$ & 3.72e-14 & $<$ 2.2e-16  \\
%  Cohen's $d$ & $\hookrightarrow$ & \textbf{0.86} & \textbf{1.32}\\
%\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions in UDC data} %, and editions and selections.}
%  Cohen's $d$ & $\hookrightarrow$ & \textbf{0.21} & \textbf{0.44}\\
%Similar results occur when we look at the edit ratio (Figures \ref{fig:box_dur_events} and \ref{fig:box_dur_events_udc}): the edit ratio is smaller in sessions that have prolonged interruptions, compared to the ones that only have short interruptions. At the bottom of the effect size (Tables \ref{tbl:p_value2} and \ref{tbl:p_value2_udc}), we show the statistical and practical significance of these results. In Mylyn, we observe large effect sizes when comparing sessions who do not have interruptions with ones that do have, and larger effect sizes for sessions with at least one longer interruption.
%These findings seem to indicate that the inverse relationship between productivity and time of duration is more pronounced in session with at least one longer interruption. This agrees with the literature for information workers.

>>>>

\usepackage{graphics}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{theorem}
\usepackage{verbatim} % comentarios
\usepackage{amsmath}
%\usepackage{algorithm}
%\usepackage{algpseudocode}
\usepackage{mwe}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage[export]{adjustbox}
\usepackage{multirow}
\usepackage{bigstrut}

\usepackage{array}
\newcommand\RR[1]{\textbf{Romain}{#1}}

@@

%First, we analyzed the number of interruptions over the productivity. In this sense, 
We split the data in five groups: The first group contains all the sessions without interruptions (\textit{none}). For the others groups, we have considered four ranges of number of interruptions delimited by their quartiles; the results differ between Mylyn and UDC, existing more interruptions per session in the former (Table \ref{tbl:quartil_int}). Then, for each group, we display the distribution of events per minute and edit ratio via boxplots. We can see the results with Mylyn in Figure \ref{fig:box_int_events}), and for UDC in Figure \ref{fig:box_int_events_udc}.

@@

In this section we analyze whether or not the interruption duration is a factor in the relationship between interruptions and developer productivity. Under the hypothesis that prolonged interruptions require more time to recover, we have built three groups of sessions based on the proportion of long interruptions. As we described previously about the kind of interruptions we consider, a prolonged interruption are those whose duration is $\geq$12 minutes, and could be due to an extended interruption, a coffee break or meeting.

The proportion of long interruptions is calculated as the sum of interruptions longer than 11 minutes, divided by the total of interruptions in that session. Then, we obtain the quantiles of the distribution of this proportion and use them to create 3 groups described like the following:

\begin{itemize}
\item \textit{low}: the first group consists of sessions where the proportion of prolonged interruptions is $<$0.30, which includes sessions with proportion equal to zero, that is sessions with only short interruptions. These sessions constitute 47.7\% in Mylyn and 20.8\% in UDC, from the total of sessions in both datasets.
\item \textit{medium}: the second group consists of sessions with a proportion between 0.30 and 0.50. These sessions constitute 31.8\% in Mylyn and 18.9\% in UDC.
\item \textit{high}: the sessions in this group have a proportion $>$0.50, which are the 20.5\% in Mylyn and 60.1\% in UDC.
\end{itemize}

Following the conclusions on RQ1, the number of interruptions may affect the results if we ignore that variable. So, we split every group in accordance to the number of interruptions; this time, instead of taking the quantiles of the distribution we took the terciles. Also, we separated the sessions with one interruption into new group. Thus, for the three metrics, we created the groups low, medium and high, and every group was split in other four groups according to the terciles of the distribution of the number on interruptions.

The Figure \ref{tbl:mylyn_stats_dur_int} shows the median of the metrics when grouping the sessions by the number of interruptions and the proportion of prolonged interruptions with Mylyn, and the Figure \ref{tbl:udc_stats_dur_int} with UDC. In this context, it is better to have a low number of interruptions (group [2-3]) and a low proportion of prolonged interruptions, and the results agree with this statement. For example, when having between 2 to 3 interruptions and a low proportion the metrics show higher values when compared to having $>$ 6 interruptions and a high proportion of prolonged interruptions. Moreover, if we focus on a category we can see a gradual decrease as the number of interruptions increases, which lead us to conclude that the proportion of prolonged interruptions has an effect on the developer productivity. In the Figures the color of lines represent a classification of the proportion of prolonged interruptions, being the green line the \textit{low} type, blue the \textit{medium} and red the \textit{high}.

The difference between categories seems to decrease when reaching higher values. There is a clear difference between the low and medium categories of proportions, but the difference between medium and high is minor. The same happens when comparing the categories [2-3] and [4-6] of the number of interruptions, and the categories [4-6] and $>$6. In other words, as the value of the metrics get higher, the negative effect (according to these metrics) changes at a very low rhythm.

Sessions with only one interruption do not belong to the medium category, for they can only contain either one short interruption (low category) or one prolonged interruption (high category). So, in the Tables the medium category shows an NA in sessions with one interruption. Also, there is an important difference in this instance as the metrics show better results in sessions in the low category, which is another evidence of the detrimental effect of prolonged interruptions.

%Comparing the results between the datasets, UDC seems to show a more defined difference between groups. The sessions with a low proportion of prolonged interruption has a greater difference (higher productivity) than sessions with medium proportion. In Mylyn this difference is more subtle but can be identified, although when having more than 6 interruptions there is not a real difference.

\begin{table}
	\tiny
	\renewcommand{\arraystretch}{2.8}
	\caption{Median for the edits per minute, selections per minute and edit ratio according to the number of interruptions and the proportion of prolonged interruptions in Mylyn.}
	\label{tbl:mylyn_stats_dur_int}
	\centering
	\begin{tabular}{|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|c|}

		\hline 
		& \multicolumn{6}{c|}{Number of interruptions} \\
		\hline
		Proportion of long int. & none & 1 & [2-3] & [4-6] & $>$6 & \\  
		\hline 
		\multicolumn{7}{c}{\textit{Edits per minute}} \\
		\hline
		low & 6.56 & 4.48 & 1.09 & 0.73 & 0.62 &  \multirow{3}{*}{\includegraphics[valign=m,scale=0.23]{figures/lines_dur_emin} } \\
		\cline{1-6}
		medium & 6.56 & NA & 0.84 & 0.69 &  0.59 &  \\		
		\cline{1-6}		
		high  & 6.56 & 1.25 & 0.66 & 0.53 & 0.60 & \\
		\hline
		\multicolumn{7}{c}{\textit{Selections per minute}} \\
		\hline 
		low &  4.56 & 3.35 & 2.13 & 1.76 & 1.34 & \newline 
		\multirow{3}{*}{\includegraphics[valign=m,scale=0.23]{figures/lines_dur_smin} }\newline \\
		\cline{1-6}
		medium & 4.56 & NA & 1.85 & 1.52 & 1.26 &  \\
		\cline{1-6}				
		high & 4.56 & 2.34 &  1.55  & 1.60 & 1.26 & \\
		\hline
		\multicolumn{7}{c}{\textit{Edit ratio}} \\
		\hline 
		low & 0.56 & 0.48 & 0.36 & 0.31  & 0.32 &  \newline 
		\multirow{3}{*}{\includegraphics[valign=m,scale=0.23]{figures/lines_dur_eratio} }\newline\\
		\cline{1-6}
		medium & 0.56 & NA & 0.34 & 0.32 & 0.32 & \\
		\cline{1-6}				
		high & 0.56 & 0.37 & 0.31 & 0.30 & 0.33 & \\
		\hline
	\end{tabular}
\end{table}

\begin{table}
\tiny
\renewcommand{\arraystretch}{2.8}
\caption{Median for the edits per minute, selections per minute and edit ratio according to the number of interruptions and the proportion of prolonged interruptions in UDC.}
\label{tbl:udc_stats_dur_int}
\centering
\begin{tabular}{|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|c|}

	  \hline 
	  & \multicolumn{6}{c|}{Number of interruptions} \\
	  \hline
	Proportion of long int. & none & 1 & [2-3] & [4-6] & $>$6 & \\  
	  \hline 
	\multicolumn{7}{c}{\textit{Edits per minute}} \\
		\hline
		low & 3.58 & 3.00 & 2.28 & 1.45 & 1.36 &  \multirow{3}{*}{\includegraphics[valign=m,scale=0.23]{figures/udc_lines_dur_emin} } \\
		\cline{1-6}
		medium & 3.58 & NA & 1.25 & 1.15 &  1.27 &  \\		
		\cline{1-6}		
		high  & 3.58 & 1.42& 1.13 & 1 & 0.94  & \\
		\hline
	\multicolumn{7}{c}{\textit{Selections per minute}} \\
	    \hline 
		low &  2.54 & 2.34 & 2.06 & 1.6 & 1.44 & \newline 
		\multirow{3}{*}{\includegraphics[valign=m,scale=0.23]{figures/udc_lines_dur_smin} }\newline \\
		\cline{1-6}
		medium & 2.54 & NA & 1.5 & 1.5 & 1.41 &  \\
		\cline{1-6}				
		high & 2.54 & 1.64 &  1.5  & 1.45 & 1.36 & \\
	    \hline
	 \multicolumn{7}{c}{\textit{Edit ratio}} \\
	   \hline 
		low & 0.57 & 0.57 & 0.52 & 0.47  & 0.46 &  \newline 
		\multirow{3}{*}{\includegraphics[valign=m,scale=0.23]{figures/udc_lines_dur_eratio} }\newline\\
		\cline{1-6}
		medium & 0.57 & NA & 0.45 & 0.44 & 0.46 & \\
		\cline{1-6}				
		high & 0.57 & 0.50 & 0.44 & 0.42 & 0.44 & \\
	   \hline
\end{tabular}
\end{table}

The statistical tests in Tables \ref{tbl:effect_size_dur_mylyn} and \ref{tbl:effect_size_dur_udc} show in general a low effect between the types of proportions of prolonged interruptions.

\begin{table}[ht!]
	\tiny
	\renewcommand{\arraystretch}{1.3}
	\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions in Mylyn} %, and editions and selections.}
	\label{tbl:effect_size_dur_mylyn}
	\centering
	\begin{tabular}{l | p{1cm} | p{1cm} | p{1cm} } 
		& low & medium & high  \\  
		\hline
		\multicolumn{4}{c}{\textbf{Edits}} \\
		\hline
		mean & 1.73 & 1.65 & 1.87 \\ 
		% \cline{3-4} 
		%t.test & $\hookrightarrow$& \multicolumn{2}{c}{$<$ 2.2e-16} \\
		\cline{3-4} 
		U-test & $\hookrightarrow$ & 3.71e-05 & 0.088  \\

		\cline{3-4} 
		Cohen's $d$ & $\hookrightarrow$	& \textbf{0.03} & \textbf{0.06} \\
		\hline

		\multicolumn{4}{c}{\textbf{Selections}} \\
		\hline 
		mean & 2.21 & 2.18 & 2.53\\ 
		% \cline{3-4} 
		%t.test & $\hookrightarrow$& 2.089e-08 & 8.175e-14 \\
		\cline{3-4} 
		U-test & $\hookrightarrow$ & 0.000378 & 0.2131 \\

		\cline{3-4} 
		Cohen's $d$ & $\hookrightarrow$	& \textbf{0.014} & \textbf{0.14}  \\  
		\hline
		\multicolumn{4}{c}{\textbf{Edit ratio}} \\
		\hline 
		mean & 0.36 & 0.35 & 0.34 \\ 
		%   \cline{3-4} 
		%  t.test & $\hookrightarrow$&  4.20E-12 & $<$ 2.2e-16 \\
		\cline{3-4} 
		U-test & $\hookrightarrow$ & 0.2717 & 0.1955 \\
		\cline{3-4} 
		Cohen's $d$ & $\hookrightarrow$ & \textbf{0.04} & \textbf{0.07} \\
		\hline

@@

\begin{table}[ht!]
	\tiny
	\renewcommand{\arraystretch}{1.3}
	\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions in UDC} %, and editions and selections.}
	\label{tbl:effect_size_dur_udc}
	\centering
	\begin{tabular}{l | p{1cm} | p{1cm} | p{1cm} } 
		& low & medium & high  \\  
		\hline
		\multicolumn{4}{c}{\textbf{Edits}} \\
		\hline
		mean & 2.22 & 1.94 & 2.06 \\ 
		% \cline{3-4} 
		%t.test & $\hookrightarrow$& \multicolumn{2}{c}{$<$ 2.2e-16} \\
		\cline{3-4} 
		U-test & $\hookrightarrow$ & \multicolumn{2}{c}{$<$ 2.2e-16}  \\

		\cline{3-4} 
		Cohen's $d$ & $\hookrightarrow$	& \textbf{0.12} & \textbf{0.06} \\
		\hline

		\multicolumn{4}{c}{\textbf{Selections}} \\
		\hline 
		mean & 2.03 & 1.85 & 1.97\\ 
		% \cline{3-4} 
		%t.test & $\hookrightarrow$& 2.089e-08 & 8.175e-14 \\
		\cline{3-4} 
		U-test & $\hookrightarrow$ & 3.05e-09 & 1.25e-07 \\

		\cline{3-4} 
		Cohen's $d$ & $\hookrightarrow$	& \textbf{0.11} & \textbf{0.03}  \\  
		\hline
		\multicolumn{4}{c}{\textbf{Edit ratio}} \\
		\hline 
		mean & 0.47 & 0.46 & 0.454 \\ 
		%   \cline{3-4} 
		%  t.test & $\hookrightarrow$&  4.20E-12 & $<$ 2.2e-16 \\
		\cline{3-4} 
		U-test & $\hookrightarrow$ & 2.57e-07 & 5.11e-14  \\
		\cline{3-4} 
		Cohen's $d$ & $\hookrightarrow$ & \textbf{0.11} & \textbf{0.15} \\
		\hline
